Title

### 2024-06-09 paper/main.tex
Updates

@@

Even though we have various algorithms for casual discovery, the adaption of these
algorithms in applied fields remain limited. In these applied fields, researchers 
typically prefer to construct these DAGs manually based on their domain knowledge.
We hypothesize that this preference towards manual DAG construction stems from the 
following difficulties in applying these methods to real dataset.

@@

In the case of DAGs, global testing methodology does exist such as Shipley
test, that can combine local structure tests into a single p-value test.
However, this does not give us a way to make modifications to our model. A
possible way to do this by using check which of these local tests are violated
based on the

In the cases when the DAG is an output of an algorithm or when constructed
by hand, it is vital to test these models against data and potentially modifying 
them for a better fit before using them for making any inference. Both global
and local tests for testing the fit of these models are available. However, when
the fit fails, we don't have a procedure to modify these models.

In the field of Structural Equation Models (SEMs), models are also typically
constructed by hand. Researchers typically come up with an initial model, which
then they use the data and expert knowledge to make modifications to. This
process is known as \emph{Specification Search}. One of the common ways to do
this is through \emph{modification indices} where a global fit of the model is
measured with different modification to the model.  Utilizing expert knowledge
to select the appropriate modification that gives the maximum improvement to
the global fit.

@@

Our main contributions in this papers are as follows:
\begin{enumerate}
	\item We present a measure of (conditional) assocation between mixed variables using
		canonical correlations. This mixed variable association is a generalization 
		of partial correlation to mixed variables.
	\item We present a procedure to iteratively construct and modify DAGs using expert 
		knowledge such that it improves the explained association between variables.
	\item Lastly, to assist researchers in manully constructing and modifying DAGs,
		we developed a web-based tool to iteratively modify their DAGs.
\end{enumerate}

@@

\subsection{Measures of Association}
In this section, we give a background on some of the commonly used effect size
measures in the context of CI testing.

\paragraph{$ X $ and $ Y $ are continuous}
In the case when $ \bm{Z} = \emptyset $, and when both $ X $ and $ Y $ are
continuous variables, Pearson's correlation coefficient based test can be used
which also gives an effect size measure. The p-value computation requires the
data to be normally distributed but other statistics can be used such as
Spearman's rank correlation, or Kendall's Tau.

In the case when $ \bm{Z} \neq \emptyset $, then partial correlations can be used.
In this case we first compute the residuals of $ X $ and $ Y $ using $ \bm{Z} $ as 
the predictor. We start by training two model $ X \sim \bm{Z} $ and $ Y \sim \bm{Z} $.
Then the residuals are computed for both as $ R_X = X - \hat{X} $ and $ R_Y = Y - \hat{Y} $.
After this we can do a normal non-conditional test on $ R_X $ and $ R_Y $.

\paragraph{All variables are discrete}

When $ \bm{Z} = \emptyset $, in the case of discrete variables, chi-squared test can be used. Effect size 
measures such as Cram\'er's V are available for it.

When $ \bm{Z} \neq \emptyset $, we can do stratification.

@@

\paragraph{Mixed data}
Recently multiple tests for mixed data have been proposed but they do not have
an effect size measure. We propose one based on canonical correlations.

>>>>

A lot of questions in science center around a causal understanding between 
variables. \emph{Causal Discovery} methods aim to find these casual structure
among variables from a given dataset.

@@

Even though we have many algorithms for casual discovery, the adaption of these
algorithms in applied fields remain limited. In these applied fields, researchers 
typically prefer to construct these DAGs manually based on their domain knowledge.
We hypothesize that this preference towards manual DAG construction stems from the 
following difficulties in applying these methods to real dataset.

@@

In the case of DAGs, global testing methodology does exist such as Shipley
test, that can combine local structure tests into a single p-value test.
However, this does not give us a way to make modifications to our model. A
possible way to do this by checking which of these local tests are violated.
However, this approach can quickly become diffult as the size of the network
increases. For example, the popular alarm network implies $x$ condition independence
statements.

@@

Our main contributions in this papers are as follows:
\begin{enumerate}
	\item We present a measure of (conditional) assocation between mixed variables using
		canonical correlations. This mixed variable association is a generalization 
		of some of the other association measures such as partial correlation to 
		mixed variables.
	\item We present a procedure to use this measure of association to
		iteratively modify DAGs using expert knowledge such that it
		improves the explained association between variables.
	\item Lastly, to assist researchers in manully constructing and modifying DAGs,
		we developed a web-based tool to iteratively modify their DAGs.
\end{enumerate}

@@

\subsection{Measures of Association}
As our DAG construction procedure relies on a measure of conditional
association between variables, in this section we list out some of the already
known measures for specific data types. These measure of associations are
typically the effect size of various conditional indepdnence tests but they
don't need to be. However, there are no generalized measure of association for
mixed data, that we propose in the next section. This is by no means an
exhaustive list, rather just to give an idea of what can be done.

\paragraph{Both $ X $ and $ Y $ are continuous}
Where there are no conditional variables, $ \bm{Z} = \emptyset $, Pearson's
correlation coefficient can be used as a measure of association between the
variables. This does make various assumptions such as linearity between the
variables, normal distribution for $ X $ and $ Y $, and homoscedasticity.

In the case when $ \bm{Z} \neq \emptyset $, then partial correlations can be
used. This requires using two linear regression models: $ E_X: X \sim \bm{Z} $
and $ E_Y: Y \sim \bim{Z} $. Then computing the residuals using these two
regressions as: $ R_X = X - E_X(\bm{Z}) $ and $ R_Y = Y - E_Y(\bm{Y}) $. After
this a simple correlation coefficient can be computed between $ R_X $ and $ R_Y $.

\paragraph{All $ X $, $ Y $, and $ \bm{Z} $ are discrete}

In the case of discrete variables, Cramer\'s V has been typically used as a
measure of association. When there are no conditional variables, $ \bm{Z} = \emptyset $,
Cramer\'s V can be computed directly from the contingency table.

However, when conditional variables are present, we can iterate over all
possible combinations of the conditional variables, compute the Cramer\'s V and
then lastly combine them together.

\todo[inline]{Is it even possible}

@@
